---
title: "My Assignments"
---

On this page, I showcase the assignment I conducted for the \[Spring 2026\] EMU430 Data Analytics course.

Please use the left menu to navigate through my assignments.

The most recent update to this page was made on 09/03/2026.



## 1. Load Required Package and Dataset

```{r}
library(dslabs)

data("polls_us_election_2016")
data <- polls_us_election_2016
```

---

## 2. Define Personal Variables

```{r}
my_first <- "Ceren"
my_birth_year <- 2001
```

---

## 3. Define k

```{r}
k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

This formula guarantees that **k is between 8 and 22**.

---

## 4. Display Rows from the Original Dataset

If **k is even**, show the first k rows.
If **k is odd**, show the last k rows.

```{r}
if (k %% 2 == 0) {
  head(data, k)
} else {
  tail(data, k)
}
```

---

## 5. Total Number of NA Values in the Dataset

```{r}
total_na <- sum(is.na(data))
total_na
```

---

## 6. Number of NA Values per Column (Top 8)

```{r}
na_per_column <- sort(colSums(is.na(data)), decreasing = TRUE)

head(na_per_column, 8)
```

---

## 7. Replace NA Values and Create New Dataset

Create a new dataset **without overwriting the original data**.

```{r}
new_data <- data
```

### Replace NA in Numeric Columns

```{r}
num_cols <- sapply(new_data, is.numeric)

new_data[num_cols] <- lapply(new_data[num_cols], function(x) {
  x[is.na(x)] <- my_birth_year + k
  x
})
```

### Replace NA in Character or Factor Columns

```{r}
char_cols <- sapply(new_data, function(x) is.character(x) | is.factor(x))
### instead of for-loop

new_data[char_cols] <- lapply(new_data[char_cols], function(x) {
  x <- as.character(x)
  x[is.na(x)] <- paste0(my_first, "_", k)
  x
})
```
---

## 8. Display Rows from the New Dataset

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

---

## 9. Total Remaining NA Values

```{r}
sum(is.na(new_data))
```

---

## 10. Check if Any NA Values Remain

```{r}
anyNA(new_data)
```
^>*While writing the code, I tried to stay true to the slides. In situations where I didn't know how to access the code, I used AI for assistance. In doing so, I ensured the tool was aware of the slides and didn't deviate from them.*